\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[margin=1in]{geometry}
\usepackage{parskip}
\usepackage{enumitem}

\title{Service Agreement}
\author{Suresh Hemal Warnasooriya}
\date{\today}

\begin{document}

\maketitle

\section{Parties}

This Agreement is entered into between:

\begin{itemize}[leftmargin=*]
  \item \textbf{Contractor (Party A):} Suresh Hemal Warnasooriya
  \item \textbf{Client (Party B):} Screenline Holdings (Pvt) Ltd, represented by \underline{\hspace{4.5cm}} (Software Engineer)
\end{itemize}

\section{Definitions}

\begin{itemize}[leftmargin=*]
  \item \textbf{Contractor} refers to Suresh Hemal Warnasooriya.
  \item \textbf{Client} refers to Screenline Holdings (Pvt) Ltd and its representatives.
  \item \textbf{Services} refers to the software engineering or related work performed by the Contractor under this Agreement.
\end{itemize}

\section{Terms and Conditions}

\begin{enumerate}
  \item \textbf{Engagement.} The Contractor is engaged by the Client as a part-time contractor. This Agreement does not create an employment relationship.

  \item \textbf{Hours.} The Contractor shall make himself available for a minimum of thirty (30) and a maximum of sixty (60) hours per month, unless otherwise agreed in writing.

  \item \textbf{Rate.} The Client shall pay the Contractor at the rate of LKR 4,000 (Sri Lankan Rupees Four Thousand) per hour for all approved hours worked.

  \item \textbf{Hours in excess of 60 per month.} If the Contractor is to work more than sixty (60) hours in any given month, the Contractor must request prior confirmation from the Client before performing such additional hours. Work beyond 60 hours per month shall be compensated at the same rate only when such confirmation has been obtained.

  \item \textbf{Additional developers.} The Client may arrange for additional developers to work with the Contractor as needed. The Contractor is not responsible for the compensation or payment of such additional developers. The Contractor shall charge only for the Contractor's own hours worked. The Client shall pay any additional developers engaged by the Client separately, as required.
\end{enumerate}

\section{Effective Date}

This Agreement shall become effective on \underline{\hspace{3cm}}.

\section{Signatures}

\vspace{1.5cm}
\begin{tabular}{@{}p{0.45\textwidth}p{0.45\textwidth}@{}}
  \textbf{Party A} & \textbf{Party B} \\[1cm]
  \hline
  Name: \underline{\hspace{4.5cm}} & Name: \underline{\hspace{4.5cm}} \\[0.5cm]
  Date: \underline{\hspace{4.5cm}} & Date: \underline{\hspace{4.5cm}} \\[0.5cm]
  Signature: \underline{\hspace{4.5cm}} & Signature: \underline{\hspace{4.5cm}}
\end{tabular}

\end{document}
