%-------------------------------------------------------------------------------
\section{Amendment --- Pay as you go / service charges}
%-------------------------------------------------------------------------------

\textbf{Invoice rule:} First-time domain is invoiced separately (upfront). All other services and domain renewal from year 2 onward are added into the regular monthly invoice.

\subsection*{Domains}
\textbf{Invoice:} First year --- paid upfront, separate invoice. From second year --- added into regular invoice.

\textbf{Prices (per year)}
\begin{center}
\begin{tabular}{ll}
  \hline
  Period   & Price (LKR) \\
  \hline
  Per year & 5,000       \\
  \hline
\end{tabular}
\end{center}

\subsection*{Hosting}
\textbf{Region:} Asia Pacific (Singapore).

\textbf{Features:} Edge cache bypass; manually purge edge cache; strict HTTPS; enforce MIME types on content headers; JS challenge; background processes (queues) up to 5 workers; scheduled tasks; auto hibernation; auto scaling; SSR to pre-render JS pages.

\textbf{Prices (per month)}
\begin{center}
\begin{tabular}{cccc}
  \hline
  vCPU & RAM    & Bandwidth & Price (LKR) \\
  \hline
  1    & 512 MB & 50 GB     & 2,500       \\
  1    & 1 GB   & 50 GB     & 3,000       \\
  2    & 512 MB & 100 GB    & 3,700       \\
  2    & 1 GB   & 100 GB    & 4,500       \\
  2    & 2 GB   & 100 GB    & 5,500       \\
  \hline
\end{tabular}
\end{center}
\textbf{Notes:} More vCPU / RAM / Bandwidth plans and more regions available on request.

\subsection*{Broadcasting channels}
\textbf{Prices (per month)}
\begin{center}
\begin{tabular}{ccr}
  \hline
  Concurrent connections & Messages per day & Price (LKR) \\
  \hline
  100                    & 200,000          & 1,000       \\
  500                    & 1,000,000        & 20,000      \\
  \hline
\end{tabular}
\end{center}

\subsection*{Database}
\textbf{Features:} Scale to zero when inactive. Storage metered hourly and summed over the month --- pay for actual use only, not maximum size reached.

\textbf{Compute:} Compute Usage = 4 GB RAM $\times$ number of hours.

\textbf{Prices}
\begin{center}
\begin{tabular}{llr}
  \hline
  Component               & Unit     & Price (LKR) \\
  \hline
  Compute usage           & per unit & 70          \\
  Storage                 & per GB   & 250         \\
  Public network transfer & per GB   & 250         \\
  \hline
\end{tabular}
\end{center}
\textbf{Notes:} Available in multiple regions; more regions on request.

\subsection*{Cache}
\textbf{Limits:} 10,000 commands/second; request size 10 MB; record size 100 MB; data size 100 GB; bandwidth unlimited.

\textbf{Prices}
\begin{center}
\begin{tabular}{llr}
  \hline
  Component & Unit      & Price (LKR) \\
  \hline
  Commands  & per 100k  & 150         \\
  \hline
\end{tabular}
\end{center}
\textbf{Notes:} Available in multiple regions; more regions on request.

\medskip
\noindent\textit{Other pay-as-you-go services and rates to be listed below as agreed.}
