%-------------------------------------------------------------------------------
\subsection{Engagement and commercial terms}
%-------------------------------------------------------------------------------
  \item \textbf{Engagement.} The Contractor is engaged as a part-time contractor. No employment relationship is created.

  \item \textbf{Hours.} The Contractor shall make themselves available for a minimum of 30 hours and a maximum of 60 hours per month, unless otherwise agreed in writing.

  \item \textbf{Rate.} The Client shall pay the Contractor at the rate of LKR 4,000 (Sri Lankan Rupees Four Thousand) per hour for all approved hours worked. This rate applies only to this Agreement and only for the period ending 2026-12-31. Work outside this Agreement or after that date may be at a different rate.

  \item \textbf{Hours over 60 per month.} If the Contractor will work more than 60 hours in any month, the Contractor must request and obtain prior confirmation from the Client before doing so. Work beyond 60 hours is paid at the same rate only when such confirmation has been obtained.

  \item \textbf{Additional developers.} The Client may arrange for additional developers to work with the Contractor. The Contractor is not responsible for their compensation. The Contractor charges only for the Contractor's own hours. The Client pays any such additional developers separately as needed.

  \item \textbf{External service charges.} The hourly rate does not cover any external service charges. Such charges (if any) are separate and to be agreed or billed separately.
