%-------------------------------------------------------------------------------
\subsection{Meetings, communication and availability}
%-------------------------------------------------------------------------------

  \item \textbf{Meetings.} As a part-time contractor, the Contractor is not available for meetings during standard working hours. The Contractor can join meetings on mercantile holidays and on weekends; on-site meetings may be held on such days. Otherwise, meetings are preferred in the evening (after 8:00 p.m.).

  \item \textbf{Quick calls and standups.} The Client may choose a formal communication medium for project communication (such as Slack, Microsoft Teams, or another agreed tool), and this medium shall be used for daily standups, scheduled meetings, and other formal communication; WhatsApp shall not be used as the formal communication channel. During working hours, short calls are acceptable but must be kept under 15 minutes and may be conducted via WhatsApp for quick checks, rescheduling discussions, or developer issue discussions. Any standup meetings must be scheduled after 8:00 p.m.

  \item \textbf{Unavailability.} If the Contractor is not available to work on any day, the Contractor shall notify the Client at least one (1) day in advance.

  \item \textbf{Support from additional developers.} Any additional developer working on the code may contact the Contractor at any time via WhatsApp regarding code-related issues. The Contractor is not obliged to respond; whether and when the Contractor responds depends on the Contractor's own situation and availability.

  \item \textbf{Progress updates.} The Contractor is responsible for keeping the Client informed about the project. The Contractor shall provide the Client with a progress update at least every other day.

  \item \textbf{Project management tool.} If the Client has a preferred project management tool, the Contractor is willing to join it and maintain project status there so that information remains up to date.
