%-------------------------------------------------------------------------------
\subsection{Term, termination and handover}
%-------------------------------------------------------------------------------

  \item \textbf{Term and payment review.} This Agreement remains in effect until the project is finished or until terminated with 14 calendar days' notice under item 28. When the project is close to ending, the Contractor will notify the Client that the project is nearing completion. The payment terms (including rate and invoicing) must be reviewed at least once every year and may be updated by mutual agreement. There is no charge for any period in which the Contractor did not perform work (pay-as-you-go services under the Amendment are excluded and may be charged as set out in the Amendment).

  \item \textbf{Termination---notice and handover.} Either party may end this Agreement only by giving the other party 14 calendar days' notice in writing. The Contractor will fully hand over the codebase (and transfer full control/ownership as per this Agreement) only when all payments due to the Contractor have been made. Until then, the Contractor retains control of the codebase and does not hand it over. The Contractor must remain as repository administrator on GitHub until all such payments are complete; only after that will admin rights be transferred or released as agreed. No charge applies for any period in which the Contractor did not perform work (pay-as-you-go services under the Amendment are excluded and may be charged as set out in the Amendment).
