%-------------------------------------------------------------------------------
\subsection{Scope, delivery and requirements}
%-------------------------------------------------------------------------------

  \item \textbf{Testing environments and deployment.} The Client shall provide testing environments. The Contractor will deliver the codebase to the Client. The Contractor has no responsibility for or involvement in the deployment process or related infrastructure.

  \item \textbf{Contractor-hosted testing environment (optional).} Alternatively, the Contractor may host a testing environment at the Contractor's own setup. In that case, the Contractor will charge for those hosting/services separately. Service charge pricing for such hosting will be set out in the Amendment to this Agreement.

  \item \textbf{Serverless vs non-serverless.} Before development begins, the Client must confirm whether the application is to be serverless or not. Any change to this (e.g.\ from serverless to server-based, or vice versa) after completion of the work will be treated as new work and charged separately.

  \item \textbf{Single point of contact for requirements.} The Client shall designate one person responsible for delivering requirements to the Contractor. The Contractor will follow requirements only from that designated person and is not obliged to act on requirements or instructions from others who claim to know the requirements. To avoid conflict of personal interests, the Client agrees to assign and maintain this single point of contact for requirements.
